Biodiversity of Japanese Pteridophytes

### 2019-06-28 reports/japan_pteridos_biodiv.Rmd
Add analysis of breeding system

```{r load-data}
loadd(world_map)
loadd(occ_data_pteridos)
loadd(occ_data_ferns_north)
loadd(occ_data_ferns)
loadd(alpha_div_pteridos)
loadd(alpha_div_ferns_north)
loadd(alpha_div_ferns_north_south)
```

@@

>>>>

```{r load-data}
loadd(world_map)
loadd(occ_data_pteridos)
loadd(occ_data_ferns_north)
loadd(occ_data_ferns)
loadd(alpha_div_pteridos)
loadd(alpha_div_ferns_north)
loadd(alpha_div_ferns_north_south)
loadd(percent_sex_dip_ferns)
loadd(ses_pd_vs_repro_ferns)
```

@@

```{r sex-dip-ferns-map, fig.cap = "Percentage of sexual diploid fern taxa, excluding hybrids."}
make_diversity_map(
  div_data = percent_sex_dip_ferns, 
  world_map = world_map, 
  occ_data = occ_data_ferns, 
  div_metric = "percent_sex_dip",
  metric_title = "% sex. diploid"
) + scale_fill_scico(palette = "bilbao", na.value="white")
```

```{r ses-pd-vs-perc-sex-dip, fig.cap = "Correlation between percentage of sexual diploid fern taxa (excluding hybrids) and standard effect size (SES) of phylogenetic diversity (PD)."}
ggplot(ses_pd_vs_repro_ferns, aes(percent_sex_dip, ses_pd)) +
  geom_point(alpha = 0.4) +
  geom_smooth(
    method = "lm",
    size = 0.5,
    fill = "pink"
  ) +
  annotate("text", 
           x = Inf, y = Inf, 
           label = glue::glue("italic(R) ^ 2 == {ses_pd_vs_repro_ferns_r2}"),
           parse = TRUE,
           hjust = 1.2,
           vjust = 1.2) +
  labs(
    x = "% sexual diploid taxa",
    y = "SES PD"
  ) +
  jntools::standard_theme()
```
